A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-23 doc/paper1-submission/paper5.tex
Fix typo.

Our supertree method operates in a different paradigm.  Phylogeny estimation is an explicit non-goal of our supertree algorithm.  We do not claim that the supertree is more accurate than the input trees it summarizes, and so conflict resolution is not a primary aim of the method. Most of our input trees have non-overlapping taxon sets, and so conflict resolution is not the primary problem.  Instead, seek to merge and aggregate phylogenetic information on the largest possible scale.  Therefore, the primary aim of our supertree method is to \emph{summarize and represent} the input trees, even when they conflict with each other.  The annotations file constructed by our pipeline is essential output because it includes information about conflict with our supertree as well as support for it.

>>>>

Our supertree method operates in a different paradigm.  Phylogeny estimation is an explicit non-goal of our supertree algorithm.  We do not claim that the supertree is more accurate than the input trees it summarizes, and so conflict resolution is not a primary aim of the method. Most of our input trees have non-overlapping taxon sets, and so conflict resolution is not the primary problem.  Instead, we seek to merge and aggregate phylogenetic information on the largest possible scale.  Therefore, the primary aim of our supertree method is to \emph{summarize and represent} the input trees, even when they conflict with each other.  The annotations file constructed by our pipeline is an essential for this task because it includes information about conflict with our supertree as well as support for it.
